%-----------------------------------------------------------------------------------------------------------------------------------------------%
%   Academic CV – COST Action ANTICIPATE
%   Adapted for Lainey Ward
%-----------------------------------------------------------------------------------------------------------------------------------------------%

\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%   PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[unicode]{hyperref}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\newcolumntype{C}{>{\centering\arraybackslash}X}

%----------------------------------------------------------------------------------------
%   BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}
{\fontfamily{lmss}\selectfont

%----------------------------------------------------------------------------------------
%   HEADER
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Lainey Ward} \\[6pt]

PhD Student | Decarb-AI Centre | Innovate for Ireland iScholar \\[3pt]
School of Civil Engineering, University College Dublin \\[6pt]

\href{https://github.com/LaineyLouiseWard}{\raisebox{-0.05\height}\faGithub\ LaineyLouiseWard}
\ $|$ \
\href{https://linkedin.com/in/lainey-ward-482821388}{\raisebox{-0.05\height}\faLinkedin\ Lainey Ward}
\ $|$ \
\href{mailto:lainey.ward1@ucdconnect.ie}{\raisebox{-0.05\height}\faEnvelope\ lainey.ward1@ucdconnect.ie}
\ $|$ \
\href{tel:+353851953317}{\raisebox{-0.05\height}\faMobile\ +353\space 85 195 3317}
\end{tabularx}

%----------------------------------------------------------------------------------------
%   SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}

PhD student at the University College Dublin Decarb-AI Centre (“Decarbonising Ireland: AI-powered pathways to climate resilience”) and an Innovate for Ireland iScholar, researching subseasonal-to-seasonal predictability of multi-hazard weather and climate events with a focus on machine-learning methods.
\par\vspace{10pt}
%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Education}

\begin{tabularx}{\linewidth}{@{}l X@{}}
2024 -- 2028 &
\textbf{Doctor of Philosophy (PhD)} \\
& Decarb-AI, School of Civil Engineering, University College Dublin \\
& Supervisors: Dr. Fiachra O'Loughlin (Primary), Dr. Conor Sweeney \\
& Thesis: Predictability of multi-hazard weather and climate events on subseasonal-to-seasonal timescales using machine learning \\

\multicolumn{2}{@{}l@{}}{\vspace{0.5cm}} \\

2023 -- 2024 &
\textbf{MSc Atmosphere, Ocean and Climate} -- \textbf{Distinction} \\
& Department of Meteorology, University of Reading \\
& Class: \textbf{Distinction} \\
& Dissertation: Quantifying long-duration storage capacity and meteorological drivers of net-zero electricity systems \\
& Relevance: atmospheric and ocean dynamics, physical meteorology, numerical modelling, and weather forecasting. \\
& Award: UK Met Office MSc Dissertation Prize \\

\multicolumn{2}{@{}l@{}}{\vspace{0.5cm}} \\

2018 -- 2022 &
\textbf{B.Sc. Physics} \\
& University College Dublin \\
& Class: \textbf{2:1} \\
& Dissertation (A+): Computational analysis of water-harvesting materials; resulting in co-authorship of a Q1 peer-reviewed publication. \\
& Award: UCD Entrance Scholar (2018) \\

\multicolumn{2}{@{}l@{}}{\vspace{0.4cm}}
\end{tabularx}

%----------------------------------------------------------------------------------------
%   WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Work Experience}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Aeronautical Meteorological Officer, Met Éireann} & Sep 2024 -- Sep 2025 \\[3pt]
\multicolumn{2}{@{}X@{}}{
Provided operational aviation weather services in compliance with ICAO and EU regulations.
Supported the Aviation Modernisation and Automation Project and contributed to data-rescue
initiatives.} \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Tutor and Demonstrator, University College Dublin} & Jan 2025 -- Present \\[3pt]
\multicolumn{2}{@{}X@{}}{
Delivered tutorials and practical sessions supporting undergraduate programming and
mathematical skills, including problem-solving and assignment guidance.} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%   Publications
%----------------------------------------------------------------------------------------
\newpage
\section{Publications}

\textbf{Ward, L.}, Forero-Martinez, N., Cortés-Huerto, R., \& Ballone, P. (2022).
Water harvesting by thermoresponsive ionic liquids: A molecular dynamics study of the water
absorption kinetics and the role of nanostructuring.
\emph{The Journal of Physical Chemistry B}, 127(24), 5494--5508.
\href{https://doi.org/10.1021/acs.jpcb.3c01655}{https://doi.org/10.1021/acs.jpcb.3c01655}
\par\vspace{10pt}
%----------------------------------------------------------------------------------------
%   SKILLS & COMPETENCIES
%----------------------------------------------------------------------------------------
\section{Skills \& Competencies}

\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming &
Proficient in Python for scientific computing, data analysis, numerical modelling, and
machine learning; experience with MATLAB and R; experienced with Git and HPC computing
clusters. \\
\multicolumn{2}{@{}l@{}}{\vspace{0.3cm}} \\

Machine Learning &
Applied machine-learning methods in atmospheric and climate contexts, including clustering,
feature-based analysis, and deep-learning models (e.g. CNNs, LSTMs, and Vision Transformers). \\
\multicolumn{2}{@{}l@{}}{\vspace{0.3cm}} \\

Data Analysis &
Analysis of large meteorological and climate datasets, including reanalysis and forecast
products; strong statistical analysis and visualisation skills. \\
\multicolumn{2}{@{}l@{}}{\vspace{0.3cm}} \\

Forecasting &
Operational experience in weather forecasting and interpretation of observational and
forecast products. \\
\multicolumn{2}{@{}l@{}}{\vspace{0.3cm}} \\

Communication &
Clear scientific communication through research presentations, written reports, and
undergraduate teaching. \\
\multicolumn{2}{@{}l@{}}{\vspace{0.3cm}} \\
\end{tabularx}


%----------------------------------------------------------------------------------------
%   ACHIEVEMENTS
%----------------------------------------------------------------------------------------
\section{Achievements}

\textbf{Met Office MSc Dissertation Prize} \\
Awarded for outstanding research for the MSc dissertation ``Quantifying Long-Duration Storage Capacity and the
Meteorological Drivers of Net-Zero Electricity Systems''.\par\vspace{4pt}

\textbf{UCD Entrance Scholar Award} \\
Awarded for academic excellence on entry to University College Dublin (2018).\par\vspace{4pt}

\textbf{UCD Academic Excellence Award} \\
Awarded for highest academic results (2017).\par\vspace{4pt}



\vspace{0.8cm}
\centering
\textbf{References available on request.}

\vfill
\center{\footnotesize Last updated: \today}

}
\end{document}
